The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-20 analysis/paper/paper.qmd

```{r}
#| label: extract-pdf-text
#| echo: false

# Extract text from PDFs
# On the first run, this function might take extra time as a Python environment needs to be set up

emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

-   To what extent were the topics and evolution thereof influenced by the exchange semester followed by the students?

>>>>

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache: true

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)
  write_csv(emu_theses, data_path)
} else {
  emu_theses <- read_csv(data_path)
}

@@

-   To what extent were the topics and evolution thereof influenced by the exchange semester followed by the students?
    - Use LDA clustering with 3 classes (corresponding to the three exchange universities) to see how well the clustering is aligned with where the student carried out their exchange semester. Use a confusion matrix to visualize the relation between real values and values assigned through clustering.
